Supplement to: Inferring Graphics Programs from Images

### 2017-05-18 paper.tex
Typo fix.
added bibliography for real

\subsection{Generalizing to hand drawings}
A practical application of our neural network is the automatic conversion of hand drawings into a subset of \LaTeX.
 We train the model
to generalize to hand drawings by introducing noise into the
renderings of the training target images.
We designed this noise process to introduce the kinds of variations found in hand drawings (Figure~\ref{handDrawingExamples}).~\remark{Process should be described (in supplement)}
Our neurally-guided SMC procedure
used pixel-wise distance as a surrogate for a likelihood function ($L(\cdot|\cdot)$ in section~\ref{neuralNetworkSection}).
But pixel-wise distance fares poorly on hand drawings, which never exactly match
the model's renders.
So, for hand drawings,
we \emph{learn} a surrogate likelihood function,
$L_{\text{learned}}(\cdot|\cdot)$.
The density $L_{\text{learned}}(\cdot|\cdot)$ is predicted by a convolutional network that we train to predict
the distance between two traces conditioned upon their renderings.
We train our likelihood surrogate to approximate the symmetric difference,
which is  the number of drawing commands by which to traces differ:
\begin{equation}
-\log L_{\text{learned}}(\text{render}(T_1)|\text{render}(T_2))\approx |T_1 - T_2| + |T_2 - T_1|\label{symmetricDistance}
\end{equation}
Intuitively, Eq.~\ref{symmetricDistance} says that
$L_{\text{learned}}(\cdot|\cdot)$ approximates the distance between
the trace we want and the trace we have so far.  Pixel-wise distance
metrics are sensitive to the fine details of how and exactly where
arrows, dashes, and corners are drawn -- but we wish to be invariant
to these details. So, we learn a distance metric over images that
approximates the distance metric in the search space over traces.

@@

\begin{figure}[H]
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-10.png}
    \includegraphics[width = 2cm]{figures/10-parse.png}    
    \subcaption{Noisy input}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-21.png}
    \includegraphics[width = 2cm]{figures/21-parse.png}    
    \subcaption{A graphical model}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-77.png}
    \includegraphics[width = 2cm]{figures/77-parse.png}    
    \subcaption{A figure from a deep learning textbook}
    \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-0.png}
    \includegraphics[width = 2cm]{figures/0-parse.png}    
    \subcaption{Near miss}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-38.png}
    \includegraphics[width = 2cm]{figures/38-parse.png}    
    \subcaption{Failing on a Ising model}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-34.png}
    \includegraphics[width = 2cm]{figures/34-parse.png}     
    \subcaption{Illusory contours}
    \end{minipage}
  \caption{Example drawings above model outputs. See also Fig.~\ref{firstPageExamples}}\label{lotsOfHandDrawings}~\remark{Showing `failure cases' (the last three above) out-of-context seems not great. Perhaps remind people in the caption that stochastic search can help correct some of these issues?}
\end{figure}
For each drawing we annotated a ground truth trace, and evaluated the
model by asking it to sample many candidate traces for each drawing.
For 55\% of the drawings the Top-1 most likely sample exactly matches the
ground truth; as we consider more samples the model encounters traces
that are closer to the ground truth annotation (Fig.~\ref{drawingIntersectionOverUnion}).
Because our current model sometimes makes mistakes on hand drawings,
we envision the current system working as follows:
a user sketches a diagram,
and the system responds by proposing a few candidate interpretations.
The user could then select the one closest to their intention and edit it if necessary.

@@

Similarity metric in program space:\\
\includegraphics[width = 8in]{figures/similarity.png}

Similarity metric in image space:\\
\includegraphics[width = 8in]{figures/imageSimilarity.png}

>>>>

\subsection{Generalizing to hand drawings}
A practical application of our neural network is the automatic conversion of hand drawings into a subset of \LaTeX.
 We train the model
to generalize to hand drawings by introducing noise into the
renderings of the training target images.
We designed this noise process to introduce the kinds of variations found in hand drawings (Figure~\ref{handDrawingExamples}; see supplement for details).
Our neurally-guided SMC procedure
used pixel-wise distance as a surrogate for a likelihood function ($L(\cdot|\cdot)$ in section~\ref{neuralNetworkSection}).
But pixel-wise distance fares poorly on hand drawings, which never exactly match
the model's renders.
So, for hand drawings,
we \emph{learn} a surrogate likelihood function,
$L_{\text{learned}}(\cdot|\cdot)$.
The density $L_{\text{learned}}(\cdot|\cdot)$ is predicted by a convolutional network that we train to predict
the distance between two traces conditioned upon their renderings.
We train our likelihood surrogate to approximate the symmetric difference,
which is  the number of drawing commands by which to traces differ:
\begin{equation}
-\log L_{\text{learned}}(\text{render}(T_1)|\text{render}(T_2))\approx |T_1 - T_2| + |T_2 - T_1|\label{symmetricDistance}
\end{equation}
Intuitively, Eq.~\ref{symmetricDistance} says that
$L_{\text{learned}}(\cdot|\cdot)$ approximates the distance between
the trace we want and the trace we have so far.  Pixel-wise distance
metrics are sensitive to the fine details of how and exactly where
arrows, dashes, and corners are drawn -- but we wish to be invariant
to these details. So, we learn a distance metric over images that
approximates the distance metric in the search space over traces.

@@

\begin{figure}[H]
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-10.png}
    \includegraphics[width = 2cm]{figures/10-parse.png}    
    \subcaption{Noisy input}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-21.png}
    \includegraphics[width = 2cm]{figures/21-parse.png}    
    \subcaption{A graphical model}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-77.png}
    \includegraphics[width = 2cm]{figures/77-parse.png}    
    \subcaption{A figure from a deep learning textbook}
    \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-0.png}
    \includegraphics[width = 2cm]{figures/0-parse.png}    
    \subcaption{Near miss}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-38.png}
    \includegraphics[width = 2cm]{figures/38-parse.png}    
    \subcaption{Failing on a Ising model}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-34.png}
    \includegraphics[width = 2cm]{figures/34-parse.png}     
    \subcaption{Illusory contours}
    \end{minipage}
  \caption{Example drawings above model outputs. See also Fig.~\ref{firstPageExamples}}\label{lotsOfHandDrawings}~\remark{Showing `failure cases' (the last three above) out-of-context seems not great. Perhaps remind people in the caption that stochastic search can help correct some of these issues?}
\end{figure}
For each drawing we annotated a ground truth trace, and evaluated the
model by asking it to sample many candidate traces for each drawing.
For 57\% of the drawings the Top-1 most likely sample exactly matches the
ground truth; as we consider more samples the model encounters traces
that are closer to the ground truth annotation (Fig.~\ref{drawingIntersectionOverUnion}).
Because our current model sometimes makes mistakes on hand drawings,
we envision the current system working as follows:
a user sketches a diagram,
and the system responds by proposing a few candidate interpretations.
The user could then select the one closest to their intention and edit it if necessary.

@@

\begin{figure}
  \begin{minipage}{0.4\textwidth}
  \includegraphics[width = 3in]{figures/NMF.png}
  \caption{NMF on features of the programs that were synthesized for each image. Horizontal component roughly corresponds to ``symmetry'' while vertical component roughly corresponds to ``loopyness'', with images on the diagonal having both of these.}    
    \end{minipage}\hfill
\begin{minipage}{0.4\textwidth}
  \includegraphics[width = 3in]{figures/imageSimilarity.png} 
  \caption{MDS on drawings using the learned distance metric, $L_{\text{learned}}(\cdot|\cdot)$. Drawings with similar looking parts in similar locations are clustered together.}
    \end{minipage}
  \end{figure}

### 2017-05-18 supplement.tex
supplement
added bibliography for real

% to compile a camera-ready version, add the [final] option, e.g.:
\usepackage{nips_2016}

@@

>>>>

% to compile a camera-ready version, add the [final] option, e.g.:
\usepackage{nips_2017}

@@

\section{Simulating hand drawings}

We introduce noise into the rendering process by:

\begin{itemize}
\item Rescaling the image intensity by a factor chosen uniformly at random from $[0.5,1.5]$
\item Translating the image by $\pm 3$ pixels chosen uniformly random
\item Rendering the \LaTeX~using the \verb|pencildraw| style,
  which adds random perturbations to the paths drawn by \LaTeX in a way designed to resemble a pencil.
\item Randomly perturbing the positions and sizes of primitive  \LaTeX drawing commands
  \end{itemize}
